\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-04-16 Latex/paper-resum.tex
Stylish V

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment. Furthermore, as we will see later, it is possible to obtain closed formulas for the convexity adjustment when the volatility of the Cheyette model is time dependent.

@@

\begin{remark}
We must note that (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) are exact when $\eta(t,x_t, y_t)$ is only a time dependent function, how is the case of a Hull-White model.
\end{remark}

>>>>

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment. Furthermore, as we will see later, it is possible to obtain closed formulas for the convexity adjustment when the volatility of the Cheyette model is time-dependent.

@@

\begin{remark}
We must note that (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) are exact when $\eta(t,x_t, y_t)$ is only a time-dependent function, how is the case of a Hull-White model.
\end{remark}
